\subsection{Noncommutative Geometry}
One candidate theory that tries to solve the problem of getting gravity incorporated into the SM is non commutative geometry (NCG). NCG is a mathematical description of space-time that makes each point have a spatial extension, as opposed to GR where each point is infinately localized in spacetime. In ordinary QFT position operators commute, $[ \hat x^{\mu}, \hat x^{\nu}] = 0$, this means that you can swap the positions without changing the state of the system. The idea that coordinates may not commute can be traced back to Heisenberg \cite{snyder1947qst}. Allain Connes \cite{connes1991pma} was the first to formulate a mathematical description of NCG. In 1990 he introduced a non-zero commutator between the position operators; \cite{rosendahl2008} 
\begin{equation} \label{eq:ncgtheta}
	[ \hat x^{\mu}, \hat x^{\nu}] = i \theta^{\mu \nu} = i \frac{1}{\Lambda_{\textrm{NCG}}^2} F^{\mu\nu},
\end{equation}
where $\theta^{\mu \nu}$ is a constant, real, antisymmetric tensor, $\Lambda_{\textrm{NCG}}$ is a scalar quantity which has the unit of energy and $F^{\mu\nu}$ is the antisymmetric field strength tensor from classical electrodynamics.\footnote{See section 11.9 in \cite{jackson1975cew} on covariance and special relativity in electrodynamics.} The commutator, $\theta^{\mu \nu}$, can be understood as a background field not affecting free particles but only their interactions. Therefore the non-commutative Standard Model will keep the original gauge group and particle content \cite{rosendahl2008}.
%We will later, when calculating  choose to ignore the space direction dependence induced by the field strength tensor and make the approximation $\theta = 1/\Lambda_{\textrm{NCG}}^2$, where $\Lambda_{\textrm{NCG}}$ is a scalar quantity which has the unit of energy.

\subsubsection{The minimum length scale}
By introducing a non-zero commutator between position operators the uncertanty principle becomes
\begin{equation}
\Delta \hat x^{\mu} \Delta \hat x^{\nu} \ge \frac{\theta^{\mu \nu}}{2}.
\end{equation}
We remember the analogue from QM where $\Delta x^{\mu} \Delta p^{\mu} \ge \frac{\hbar}{2}$, the better precision we have in position, the worse the precision in the momentum becomes. Another way to think of it is that if you have an accurate measure of the position of a particle, the uncertainty principle sets a lower limit, $\frac{\hbar}{2}$, to how small the disturbance on the momentum measurement can be. In the same way NCG defines a minimum length scale. Here the uncertainty of two positions conflate, and creates a minimum detectable area which is dependent on the magnitude of $\theta^{\mu \nu}$.

\subsubsection{New interactions}
The inclusion of non-commutative geometry into the standard model adds new terms to the SM Lagrangian. Specifically we want to look at a term which allows the $Z^0$ boson to interact with gluons, the mediators of the strong interaction. This amplitude is strictly zero in the ordinary SM, but in NCG we get a term in the Lagrangian which looks like \cite{melic2005smn}
\begin{align} \label{eq:zggterm}
	\mathcal{L}_{Zgg} = &\frac{e}{4}\sin{2\theta_W}\textrm{K}_{Zgg}\theta^{\rho\sigma}
	[2 Z^{\mu\nu} (2 G_{\mu\rho}^a G_{\nu\sigma}^b - G_{\mu\nu}^a G_{\rho\sigma}^b) \nonumber \\
	 &+ 8 Z_{\mu\rho} G^{\mu\nu,a} G_{\nu\sigma}^b - Z_{\rho\sigma} G_{\mu\nu}^a G^{\mu\nu,b}
	] \delta^{ab},
\end{align}

where $K_{Zgg}$ is a dimensionless constant in the region $\{-0.1,0.2\}$ \cite{behr2003dnc}, $\theta_W$ is the Weinberg angle and $\theta^{\rho\sigma}$ is given in \eqref{eq:ncgtheta}. Using this term one can derive the corresponding feynman rules, arriving at a non-zero amplitude for process including $Z^0gg$ vertices \cite{melic2005smn}. These vertices are of special interest because they are allowed for by on-shell propagators. This is in contrast to processes like $Z \rightarrow ZZ$ and $Z \rightarrow Z\gamma$, which are forbidden, in the off-shell domain, by kinematics \cite{behr2003dnc}.